Untitled

### 2025-03-11 code/manuscript_altanalysis.Rmd
final figures

df.temptemp <- df.temptemp %>%
  left_join(uds.cw %>% filter(Year == 2011) %>% select(ModernGranteeID, BHCMIS.ID:PH), by = c("BHCMIS ID" = "BHCMIS.ID")) %>%
  left_join(coredata %>% select(GrantNumber, UrbanRuralFlag), by = c("ModernGranteeID" = "GrantNumber")) %>% 
  mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
                    (STATE %in% c('PA','IN','AK') & Year >= 2015) |
                    (STATE %in% c('MT','LA') & Year >= 2016) |
                    (STATE %in% c('VA','ME') & Year >= 2019) |
                    (STATE %in% c('ID','UT','NE') & Year >= 2020) |
                    (STATE %in% c('OK','MO') & Year >= 2021) |
                    (STATE %in% c('AZ','AR','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))

@@

@@

@@

   model <-  did2s(
      data = df.temptemptemp,
      yname = "Outcome",
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>=2, 1, 0), ref = FALSE),
        #second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_min)) ,
        cluster_var = "ID",
      verbose = TRUE
    )

@@

## Stratified figure instead of table 
```{r}

@@

@@

@@

>>>>

df.temptemp <- df.temptemp %>%
  left_join(uds.cw %>% filter(Year == 2011) %>% select(ModernGranteeID, BHCMIS.ID:PH), by = c("BHCMIS ID" = "BHCMIS.ID")) %>%
  left_join(coredata %>% select(GrantNumber, UrbanRuralFlag), by = c("ModernGranteeID" = "GrantNumber")) %>% 
  mutate(ACA = ifelse((STATE %in% c('MI','NH') & Year >= 2014) |
                    (STATE %in% c('PA','IN','AK') & Year >= 2015) |
                    (STATE %in% c('MT','LA') & Year >= 2016) |
                    (STATE %in% c('VA','ME') & Year >= 2019) |
                    (STATE %in% c('ID','UT','NE') & Year >= 2020) |
                    (STATE %in% c('OK','MO','AR') & Year >= 2021) |
                    (STATE %in% c('SD','NC') & Year >= 2023) | 
                    (STATE %in% c('AZ','CA','CO','CT','DE','DC','HI','IL','IA','KY','MD','MA','MN','NV','NJ','NM','NY','ND','OH','OR','PA','RI','VT','VA','WA') & Year >= 2014), 1, 0))

@@

#ggsave(filename = "Figure1.pdf", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Revision 1", plot = p.desc, width = 7, height = 10)
```

@@

ggsave(filename = "Figure2.pdf", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Revision 1", plot = ess + theme(legend.position="none"), width = 8, height = 10)

@@

   model <-  did2s(
      data = df.temptemptemp,
      yname = "Outcome",
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>=2, 1, 0), ref = FALSE),
        #second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_min)) ,
        cluster_var = "ID",
      verbose = TRUE
    )

@@

## Stratified figure instead of table - optional
```{r}

@@

strat.temp <- strat.temp %>% 
  select(Outcome) %>% 
  cbind(data.frame(rbind(c(1.82, -0.4, 4.04),
      c(-448, -2513, 1617), 
      c(-0.08, -0.33, 0.16), 
      c(6.30, 0.4, 12.2), 
      c(-0.18, -0.71, 0.34),

      c(NA, NA, NA), 
      c(2.33, 0.03, 4.63), 
      c(-2.92, -5.4, -0.44), 
      c(NA, NA, NA), 
      c(-0.25, -0.73, 0.23),

      c(-0.31, -0.75, 0.14), 
      c(-0.37, -2.42, 1.68), 
      c(4.75, -0.64, 10.14), 
      c(2.49, -18.84, 23.82), 
      c(-1.22, -3.48, 1.03),

      c(-3.31, -5.65, -0.96), 
      c(4701, 1533, 7869) , 
      c(-0.37, -0.65, -0.09), 
      c(4.43, -1.92, 10.78), 
      c(-0.69, -1.08, -0.31),

      c(NA, NA, NA), 
      c(5.75, 3.46, 8.04), 
      c(-3.17, -5.32, -1.01), 
      c(NA, NA, NA), 
      c(-0.99, -1.50, -0.48),

      c(-0.67, -1.09, -0.24), 
      c(-1.25, -2.87, 0.37), 
      c(5.36, 1.62, 9.11), 
      c(81.13, 46.12, 116.14), 
      c(1.67, 0.62, 2.73)))  * 100 / as.numeric((df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Qcomp, Total, Altman, logPatsPerStaff, Complexity, Intensity, Pct.MCD, Pct.None, CostPerPat, quick_ratio, months_of_cash, Profitability, LiabPctAssets, Staff) %>% 
  summarise_all(mean.nas) %>% 
  filter(Post == 0 & Treat == "Treated") %>% 
  t() %>% 
    rbind(100))[-c(1,2),])

) %>% 
  rename(Estimate = X1, 
         LB = X2, UB = X3) %>% 
  cbind(strat.temp %>% 
  select(Class, Measure))

@@

ggsave(filename = "Figure3.pdf", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Revision 1", plot = p + theme(panel.spacing = unit(1, "lines"),  strip.text = element_text(face = "bold", size = 12)), width = 8, height = 10)

@@

coeffs.did.ACA <- rep(0, 8)

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp %>% inner_join(df.temptemptemp %>% group_by(`BHCMIS ID`) %>% summarise(ACA = max(ACA)) %>% filter(ACA == 1), by = c("BHCMIS ID")) %>% filter(Year < 2024),  
      #data = df.temptemptemp %>% filter(ACA == 0 & Year <= 2024), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min >= 2, 1, 0), ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did.ACA <- rbind(coeffs.did.ACA, c(model$coeftable[1,], model$coeftable[2,]))

core.did.estimates.ACA <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.ACA[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Pr...t.., Estimate.1, `95% CI.1`, `Pr...t...1`)

coeffs.did.nonACA <- rep(0, 8)

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp %>% inner_join(df.temptemptemp %>% group_by(`BHCMIS ID`) %>% summarise(ACA = max(ACA)) %>% filter(ACA == 0), by = c("BHCMIS ID")) %>% filter(Year < 2024),  
      #data = df.temptemptemp %>% filter(ACA == 0 & Year <= 2024), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min >= 2, 1, 0), ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did.nonACA <- rbind(coeffs.did.nonACA, c(model$coeftable[1,], model$coeftable[2,]))

core.did.estimates.nonACA <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.nonACA[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Pr...t.., Estimate.1, `95% CI.1`, `Pr...t...1`)

core.did.estimates.nonACA <- core.did.estimates.nonACA
#rownames(core.did.estimates) <- NULL

cbind(core.did.estimates.ACA, core.did.estimates.nonACA)

df.temptemptemp %>% inner_join(df.temptemptemp %>% group_by(`BHCMIS ID`) %>% summarise(ACA = max(ACA)), by = c("BHCMIS ID")) %>% 
  mutate(value = ifelse(value_min == 1, 0, 1)) %>% 
  ungroup() %>% 
  select(ACA.y, value) %>% 
  group_by(ACA.y, value) %>% 
  summarise(n())
